On the presentation of orthogonal groups over polynomial rings

### 2019-06-05 dl-paper.tex
Added Lemma 34

\begin{corollary}
  $T_\alpha$ satisfy the relations $\text{R3}_{1,1}$ in the remaining case when $\alpha$ is perpendicular to $\beta$.
\end{corollary}

@@

\begin{align*} x_{\alpha+\beta+\gamma}(abX^{-1}) = {}^{x_{-\beta}(X^{-1})}\!x_{\alpha+\beta+\gamma}(abX^{-1}) & \text{ by the above relation}\\
 = {}^{x_{-\beta}(X^{-1})}\![x_{\alpha+\beta}(b'), x_\gamma(aX^{-1})] & \text{ by R$2_1$} \\
 = [x_{\alpha}(b'X^{-1}) x_{\alpha+\beta}(b'), x_\gamma(aX^{-1})] & \text{ by R$2_1$ and R$3_1$ for sharp angles }\\
 = {}^{x_{\alpha}(b'X^{-1})}\!x_{\alpha+\beta+\gamma}(abX^{-1}) [x_{\alpha}(b'X^{-1}), x_\gamma(aX^{-1})] & \text{ by R$2_1$} \\
 = x_{\alpha+\beta+\gamma}(abX^{-1}) [x_{\alpha}(b'X^{-1}), x_\gamma(aX^{-1})] & \text{ by R$3_1$ for sharp angles.} \end{align*}

>>>>

\begin{comment}
$n \geq m$
$b = \epsilon  X^{-m}$
$\epsilon \in R^*$, $d \in R$
$abc = d X^{-n}$

$|a| = n-m$, $|b| = m$, $|c| = 0$

\begin{align*}
[x_{il}(abc), x_{jk}(b)] &= 1 & \text{R3}_{n,m} \\
[x_{ij}(a), x_{kl}(c)] &= 1 & \text{R3}_{n-m, 0}\\
[x_{ik}(ab), x_{kl}(c)] &= x_{il}(abc), & \text{R2}_{n, 0} \\
[x_{jk}(b), x_{kl}(c)] &= x_{jl}(bc), & \text{R2}_{m, 0}\\
[x_{ij}(a), x_{jk}(b)] &= x_{ik}(ab), & \text{R2}_{n-m, m}\\
[x_{ij}(a), x_{jl}(bc)] &= x_{il}(abc),& \text{R2}_{n-m, m}\\
[x_{jk}(b), x_{kl}(c)] &= x_{jl}(bc), & \text{R2}_{m, 0}\\
[x_{ij}(a), x_{jk}(b)] &= x_{ik}(ab) & \text{R2}_{n-m, m}
\end{align*}
\end{comment}

\begin{lemma} For any simply laced root system $\Phi$ of rank $\geq 3$, a local ring $A$ and any $1 \leq m \leq n$ the relation $\text{R3}_{n,m}^\perp$ follows from $\text{R1}_n$, $\text{R2}_{n,0}$, $\text{R2}_{m,0}$ and $\text{R2}_{n-m,m}$ and $\text{R3}_{n-m, 0}^\perp$. \end{lemma}
\begin{proof}
We need to show that $[x_{\alpha}(cX^{n}), x_{\beta}(dX^{m})] = 1$ for all $c, d\in A$, $\alpha \perp \beta$. Notice that in the special case $c = \epsilon \in A^*$ the assertion follows from a consideration of \cite[Fig.~4]{KS99} in which one substitutes $a = \epsilon^{-1} d \cdot X^{-(n-m)}$, $b = \epsilon X^{-m}$, $c = 1$.

Now if $c \in M$ we can express it as a difference $c = \epsilon_1 - \epsilon_2$ of two invertible elements. The required assertion now follows from $\text{R1}_{n}$, the standard commutator identity $[ab, c] = {}^a[b, c] [a, c]$ and the special case considered above.
\end{proof}

\begin{comment}
\begin{corollary}
  $T_\alpha$ satisfy the relations $\text{R3}_{1,1}$ in the remaining case when $\alpha$ is perpendicular to $\beta$.
\end{corollary}

@@

\begin{align*} x_{\alpha+\beta+\gamma}(abX^{-1}) = {}^{x_{-\beta}(X^{-1})}\!x_{\alpha+\beta+\gamma}(abX^{-1}) & \text{ by the above relation}\\
 = {}^{x_{-\beta}(X^{-1})}\![x_{\alpha+\beta}(b'), x_\gamma(aX^{-1})] & \text{ by R$2_1$} \\
 = [x_{\alpha}(b'X^{-1}) x_{\alpha+\beta}(b'), x_\gamma(aX^{-1})] & \text{ by R$2_1$ and R$3_1$ for sharp angles }\\
 = {}^{x_{\alpha}(b'X^{-1})}\!x_{\alpha+\beta+\gamma}(abX^{-1}) [x_{\alpha}(b'X^{-1}), x_\gamma(aX^{-1})] & \text{ by R$2_1$} \\
 = x_{\alpha+\beta+\gamma}(abX^{-1}) [x_{\alpha}(b'X^{-1}), x_\gamma(aX^{-1})] & \text{ by R$3_1$ for sharp angles.} \end{align*}
 \end{comment}
